---
title: "Breast data processing"
author: "Shuyang"
date: "10/6/2019"
output: 
  html_document: default
  pdf_document: default
---
```{r setDefault, include=FALSE}
# This code chunk defines the default chunks setting
knitr::opts_chunk$set(eval=TRUE, comment="$$$", fig.width=6)
```
<br>
```{r eval=TRUE, results='hold'}
#library(plyr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(colorspace)
library(data.table)
library(gplots)
library( "genefilter" )
library(ggplot2)
library(NMF)
library(pkgmaker)
library(registry)
library(rngtools)
library(cluster)

library('heatmap.plus')
library('gplots')
library('RColorBrewer')
library("pheatmap")
#kde function
library(ks)
library(rgl)
library("kdensity")
```

```{r eval=TRUE, results='hold'}
setwd('/Users/dengshuyang/Desktop/Bioinfo2019/Breast_project/')
CNA_Breast <- read.csv('CNA_Breast.csv', header=TRUE)
#Phospho_Breast <- read.csv('Phospho_Breast.csv', header=TRUE)
Protein_Breast <- read.csv('Protein_Breast.csv', header=TRUE)
RNA_Breast <- read.csv('RNA_Breast.csv', header=TRUE)
```
<br>

### Rename row and col names
```{r eval=TRUE, results='hold'}
getName <- function(x){
  v <- unlist(strsplit(x, '\\.'))
  name <- paste0(v[1], '-', v[2])
  return(name)
}
```

```{r eval=TRUE, results='hold'}
getName2 <- function(x){
  w <- unlist(strsplit(x, '\\-'))
  w2 <- w[1]
  return(w2)
}
```

<br>
### columns rename
```{r eval=TRUE, results='hold'}
colnames(CNA_Breast)[2:ncol(CNA_Breast)] <- sapply(colnames(CNA_Breast)[-1], getName)
#colnames(Phospho_Breast)[2:ncol(Phospho_Breast)] <- sapply(colnames(Phospho_Breast)[-1], getName)
colnames(Protein_Breast)[2:ncol(Protein_Breast)] <- sapply(colnames(Protein_Breast)[-1], getName)
colnames(RNA_Breast)[2:ncol(RNA_Breast)] <- sapply(colnames(RNA_Breast)[-1], getName)
```
### rename the first col 
```{r eval=TRUE, results='hold'}
Protein_Breast[,1] <- sapply(as.character(Protein_Breast[,1]), getName2)
```
### and then make it the rowname of data frame

```{r eval=TRUE, results='hold'}
Protein_Breast_2 <- Protein_Breast[,-1]
rownames(Protein_Breast_2) <- make.names(Protein_Breast[,1], unique=TRUE)
Protein_Breast <- Protein_Breast_2

CNA_Breast_2 <- CNA_Breast[,-1]
rownames(CNA_Breast_2) <- make.names(CNA_Breast[,1], unique=TRUE)
CNA_Breast <- CNA_Breast_2

RNA_Breast_2 <- RNA_Breast[,-1]
rownames(RNA_Breast_2) <- make.names(RNA_Breast[,1], unique=TRUE)
RNA_Breast <- RNA_Breast_2

#Phospho_Breast_2 <- Phospho_Breast[,-1]
#rownames(Phospho_Breast_2) <- make.names(Phospho_Breast[,1], unique=TRUE)
#Phospho_Breast <- Phospho_Breast_2
```

```{r eval=TRUE, results='hold'}
#write.csv(Protein_Breast_2, file='Protein_Breast_2.csv')
#write.csv(RNA_Breast_2, file='RNA_Breast_2.csv')
#write.csv(CNA_Breast_2, file='CNA_Breast_2.csv')
```

<br>
### overlapping version
```{r eval=TRUE, results='hold'}
# overlap as Protein_match, RNA_match2, CNA_match2 by protein_breast rownames
RNA_match <- RNA_Breast[rownames(RNA_Breast) %in% rownames(Protein_Breast),]
CNA_match <- CNA_Breast[rownames(CNA_Breast) %in% rownames(Protein_Breast),]
CNA_match2 <- CNA_match[rownames(CNA_match) %in% rownames(RNA_match),]
RNA_match2 <- RNA_match[rownames(RNA_match) %in% rownames(CNA_match2),]
Protein_match <- Protein_Breast[rownames(Protein_Breast) %in% rownames(CNA_match2),]
```

```{r eval=TRUE, results='hold'}
# overlap as Protein_match, RNA_match2, CNA_match2 by protein_breast rownames
which(!(colnames(Protein_match) %in% colnames(CNA_match2)))
Protein_match2 <- Protein_match[-c(10, 68, 74, 81, 82, 83)]
```

```{r eval=TRUE, results='hold'}
## save
#write.csv(Protein_match2, file='Protein_match2.csv')
#write.csv(RNA_match2, file='RNA_match2.csv')
#write.csv(CNA_match2, file='CNA_match2.csv')
```

### missing data plot
**resource:** https://jenslaufer.com/data/analysis/visualize_missing_values_with_ggplot.html
```{r eval=TRUE, results='hold'}
colSums(is.na(Protein_match2))
print('--------------------------------')
rowSums(is.na(Protein_match2))
```

```{r eval=TRUE, results='hold'}
# Sample missing values
Protein_missdf <- Protein_match2 %>%
  gather(key = "key", value = "val") %>%
  mutate(is.missing = is.na(val)) %>%
  group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  filter(is.missing==T) %>%
  select(-is.missing) %>%
  arrange(desc(num.missing)) 
  #summarise(n = n())
```

```{r eval=TRUE, results='hold'}
CNA_missdf <- CNA_match2 %>%
  gather(key = "key", value = "val") %>%
  mutate(is.missing = is.na(val)) %>%
  group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  filter(is.missing==T) %>%
  select(-is.missing) %>%
  arrange(desc(num.missing))
```

```{r eval=TRUE, results='hold'}
RNA_missdf <- RNA_match2 %>%
  gather(key = "key", value = "val") %>%
  mutate(is.missing = is.na(val)) %>%
  group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  filter(is.missing==T) %>%
  select(-is.missing) %>%
  arrange(desc(num.missing))
```

```{r eval=TRUE, results='hold'}
Protein_missdf %>%
  ggplot() +
  geom_bar(aes(x=reorder(key, -num.missing), y=num.missing), stat = 'identity', col='#E69F00', fill='#E69F00') +
  labs(x='Samples', y="number of missing values", title='Protein samples missing values') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=5), plot.title=element_text(size=22))
```

```{r eval=TRUE, results='hold'}
RNA_missdf %>%
  ggplot() +
  geom_bar(aes(x=reorder(key, -num.missing), y=num.missing), stat = 'identity',width=1) +
  labs(x='Samples', y="number of missing values", title='RNA samples missing values') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=5), plot.title=element_text(size=22))
```


```{r eval=TRUE, results='hold'}
# Gene missing values
# get T-matrix and then convert the matrix to datafram
tProtein_match2 <- t(Protein_match2)
tProtein_match2 <- as.data.frame(tProtein_match2)
```

```{r eval=TRUE, results='hold'}
# Gene missing values
# get T-matrix and then convert the matrix to datafram
tRNA_match2 <- t(RNA_match2)
tRNA_match2 <- as.data.frame(tRNA_match2)
```

```{r eval=TRUE, results='hold'}
# Gene missing values
Protein_missdf_gene <- tProtein_match2 %>%
  gather(key = "key", value = "val") %>%
  mutate(is.missing = is.na(val)) %>%
  group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  filter(is.missing==T) %>%
  select(-is.missing) 


```

```{r eval=TRUE, results='hold'}
# Gene missing values
RNA_missdf_gene <- tRNA_match2 %>%
  gather(key = "key", value = "val") %>%
  mutate(is.missing = is.na(val)) %>%
  group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  filter(is.missing==T) %>%
  select(-is.missing) %>%
  arrange(desc(num.missing))

```

```{r eval=TRUE, results='hold'}
Protein_missdf_gene %>%
  ggplot() +
  geom_bar(aes(x=reorder(key, -num.missing), y=num.missing), stat = 'identity', width=1)+
  labs(x='gene', y="number of missing values", title='Protein genes missing values') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=1),plot.title=element_text(size=22))
```
**plot generates wide white anf grey bars, use width=1 to avoid it, which can make bars assemble together**
```{r eval=TRUE, results='hold'}
RNA_missdf_gene %>%
  ggplot() +
  geom_bar(aes(x=reorder(key, -num.missing), y=num.missing), stat = 'identity', width=1) +
  #width is used to remove color difference generated by barplot
  labs(x='gene', y="number of missing values", title='RNA genes missing values') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=1),plot.title=element_text(size=22))

```

```{r eval=TRUE, results='hold'}
#vis_miss(tProtein_match2)
```
<br>
### ERBB2 protein-rna
```{r eval=TRUE, results='hold'}
df1 <- Protein_match2['ERBB2',]
df2 <- RNA_match2['ERBB2',]
df3 <- CNA_match2['ERBB2',]
#df1_match <- df1[colnames(df2)]
df <- rbind(df1, df2)
df23 <- rbind(df2,df3)
df13 <- rbind(df1,df3)
rownames(df) <- c('ERBB2_Protein', 'ERBB2_RNA')
rownames(df13) <- c('ERBB2_Protein', 'ERBB2_CNA')
rownames(df23) <- c('ERBB2_RNA', 'ERBB2_CNA')
```
### CCNB1 protein-rna
```{r eval=TRUE, results='hold'}
cdf1 <- Protein_match2['CCNB1',]
cdf2 <- RNA_match2['CCNB1',]
cdf3 <- CNA_match2['CCNB1',]
#df1_match <- df1[colnames(df2)]
cdf <- rbind(cdf1, cdf2)
cdf23 <- rbind(cdf2,cdf3)
cdf13 <- rbind(cdf1,cdf3)
rownames(cdf) <- c('CCNB1_Protein', 'CCNB1_RNA')
rownames(cdf13) <- c('CCNB1_Protein', 'CCNB1_CNA')
rownames(cdf23) <- c('CCNB1_RNA', 'CCNB1_CNA')
```

### CENPF protein-rna
```{r eval=TRUE, results='hold'}
ddf1 <- Protein_match2['CENPF',]
ddf2 <- RNA_match2['CENPF',]
ddf3 <- CNA_match2['CENPF',]
#df1_match <- df1[colnames(df2)]
ddf <- rbind(ddf1, ddf2)
ddf23 <- rbind(ddf2,ddf3)
ddf13 <- rbind(ddf1,ddf3)
rownames(ddf) <- c('CENPF_Protein', 'CENPF_RNA')
rownames(ddf13) <- c('CENPF_Protein', 'CENPF_CNA')
rownames(ddf23) <- c('CENPF_RNA', 'CENPF_CNA')
```



```{r eval=TRUE, results='hold'}
tdf <- t(df)
tdf <- data.frame(tdf)
g1 <- ggplot(data=tdf)+
  geom_point(mapping=aes(x=tdf$ERBB2_RNA, y=tdf$ERBB2_Protein))+
  labs(x='RNA', y="Protein", title='ERBB2 RNA-protein')+
  theme(plot.title=element_text(size=22))
g1
```
```{r eval=TRUE, results='hold'}
tdf23 <- t(df23)
tdf23 <- data.frame(tdf23)
g2 <- ggplot(data=tdf23)+
  geom_point(mapping=aes(x=tdf23$ERBB2_RNA, y=tdf23$ERBB2_CNA))+
  labs(x='RNA', y="CNA", title='ERBB2 RNA-CNA')+
  theme(plot.title=element_text(size=22))
g2
```

```{r eval=TRUE, results='hold'}
#ccnb1
tcdf <- t(cdf)
tcdf <- data.frame(tcdf)
g4 <- ggplot(data=tcdf)+
  geom_point(mapping=aes(x=tcdf$CCNB1_RNA, y=tcdf$CCNB1_Protein))+
  labs(x='RNA', y="Protein", title='CCNB1 RNA-protein')+
  theme(plot.title=element_text(size=22))
g4
```

```{r eval=TRUE, results='hold'}
#ccnb1
tcdf23 <- t(cdf23)
tcdf23 <- data.frame(tcdf23)
g5 <- ggplot(data=tcdf23)+
  geom_point(mapping=aes(x=tcdf23$CCNB1_RNA, y=tcdf23$CCNB1_CNA))+
  labs(x='RNA', y="CNA", title='CCNB1 RNA-CNA')+
  theme(plot.title=element_text(size=22))
g5
```
```{r eval=TRUE, results='hold'}
tdf13 <- t(df13)
tdf13 <- data.frame(tdf13)
g3 <- ggplot(data=tdf13)+
  geom_point(mapping=aes(x=tdf13$ERBB2_CNA, y=tdf13$ERBB2_Protein))+
  labs(x='CNA', y="Protein", title='ERBB2 CNA-protein')+
  theme(plot.title=element_text(size=22))
g3
```
```{r eval=TRUE, results='hold'}
#ccnb1
tcdf13 <- t(cdf13)
tcdf13 <- data.frame(tcdf13)
g6 <- ggplot(data=tcdf13)+
  geom_point(mapping=aes(x=tcdf13$CCNB1_CNA, y=tcdf13$CCNB1_Protein))+
  labs(x='CNA', y="Protein", title='CCNB1 CNA-protein')+
  theme(plot.title=element_text(size=22))
g6
```
```{r eval=TRUE, results='hold'}
#cenpf
tddf <- t(ddf)
tddf <- data.frame(tddf)
g7 <- ggplot(data=tddf)+
  geom_point(mapping=aes(x=tddf$CENPF_RNA, y=tddf$CENPF_Protein))+
  labs(x='RNA', y="Protein", title='CENPF RNA-protein')+
  theme(plot.title=element_text(size=22))
g7
```
```{r eval=TRUE, results='hold'}
#cENPF
tddf23 <- t(ddf23)
tddf23 <- data.frame(tddf23)
g8 <- ggplot(data=tddf23)+
  geom_point(mapping=aes(x=tddf23$CENPF_RNA, y=tddf23$CENPF_CNA))+
  labs(x='RNA', y="CNA", title='CENPF RNA-CNA')+
  theme(plot.title=element_text(size=22))
g8
```
```{r eval=TRUE, results='hold'}
#cenpf
tddf13 <- t(ddf13)
tddf13 <- data.frame(tddf13)
g9 <- ggplot(data=tddf13)+
  geom_point(mapping=aes(x=tddf13$CENPF_CNA, y=tddf13$CENPF_Protein))+
  labs(x='CNA', y="Protein", title='CENPF CNA-protein')+
  theme(plot.title=element_text(size=22))
g9
```
```{r}
library(ggpubr)
ggarrange(g1,g2,g3,g4,g5,g6,g7,g8,g9 + rremove("x.text"), 
          labels = c("A", "B", "C",'D', 'E', 'F', 'G', 'H'),
          ncol = 3, nrow = 3)
          
```
# heatmap - coordinate coefficience
```{r eval=TRUE, results='hold'}
# 数据导入
setwd('/Users/dengshuyang/Desktop/Bioinfo2019/Breast_project/')
Protein_Breast <- read.csv('Protein_Breast_2.csv', stringsAsFactors = FALSE)
RNA_Breast <- read.csv('RNA_Breast_2.csv', stringsAsFactors = FALSE)
CNA_Breast <- read.csv('CNA_Breast_2.csv', stringsAsFactors = FALSE)
pam50_genes <- read.csv('pam50_genes.csv', stringsAsFactors = FALSE)
```


```{r eval=TRUE, results='hold'}
# 数据筛选
Protein_Breast <- merge(pam50_genes, Protein_Breast, by.y = 'X', by.x = 'gene') #inner join if don't use all.x=TRUE
RNA_Breast <- merge(pam50_genes, RNA_Breast, by.y = 'X', by.x = 'gene', all.x = TRUE)
CNA_Breast <- merge(pam50_genes, CNA_Breast, by.y='X', by.x='gene')
```

```{r eval=TRUE, results='hold'}
# 数据转换
row.names(Protein_Breast) <- Protein_Breast$gene
Protein_Breast <- select(Protein_Breast, -gene) 
Protein_Breast <- as.matrix(Protein_Breast)

row.names(RNA_Breast) <- RNA_Breast$gene
RNA_Breast <- select(RNA_Breast, -gene)
RNA_Breast <- as.matrix(RNA_Breast)

rownames(CNA_Breast) <- CNA_Breast$gene
CNA_Breast <- select(CNA_Breast, -gene)
CNA_Breast <- as.matrix(CNA_Breast)
```
### making heatmap
resource: https://wiki.bits.vib.be/index.php/Use_pheatmap_to_draw_heat_maps_in_R
```{r eval=TRUE, results='hold'}
# Protein-protein
col.pal <- brewer.pal(9,"Blues")
drows1 <- "euclidean"
dcols1 <- "euclidean"

hm.parameters <- list(Protein_Breast, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "Protein-Protein heatmap",
  clustering_method = "average",
  cluster_rows = TRUE, cluster_cols = TRUE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 5
  )
 
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters)
```

```{r eval=TRUE, results='hold'}
#RNA-RNA

hm.parameters2 <- list(RNA_Breast, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = 'column',
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "Protein-Protein heatmap",
  clustering_method = "average",
  cluster_rows = TRUE, cluster_cols = TRUE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 5)
 
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters2)
```

```{r eval=TRUE, results='hold'}
#CNA-CNA

hm.parameters3 <- list(CNA_Breast, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "Protein-Protein heatmap",
  clustering_method = "average",
  cluster_rows = TRUE, cluster_cols = TRUE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize=5)
 
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters3)
```

```{r eval=TRUE, results='hold'}
#Protein-RNA
#distrinct pro and rna
Protein_Breast <- read.csv('Protein_Breast_2.csv', stringsAsFactors = FALSE)
RNA_Breast <- read.csv('RNA_Breast_2.csv', stringsAsFactors = FALSE)
CNA_Breast <- read.csv('CNA_Breast_2.csv', stringsAsFactors = FALSE)
pam50_genes <- read.csv('pam50_genes.csv', stringsAsFactors = FALSE)

colnames(Protein_Breast) <- paste0(colnames(Protein_Breast), '_pro')
colnames(RNA_Breast) <- paste0(colnames(RNA_Breast), '_rna')

#pro_rna <- merge(pam50_genes, Protein_Breast, by.x = 'gene', by.y = 'X_pro', all.x = TRUE)
#pro_rna <- merge(pro_rna, RNA_Breast, by.x = 'gene', by.y = 'X_rna', all.x = TRUE)

#row.names(pro_rna) <- pro_rna$gene
#pro_rna <- select(pro_rna, -gene)
#pro_rna <- as.matrix(pro_rna)
 
```
<br>
```{r eval=TRUE, results='hold'}
#Protein-RNA

hm.parameters4 <- list(pro_rna, 
  color = col.pal,
  cellwidth = 5, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "Protein-Protein heatmap",
  clustering_method = "average",
  cluster_rows = TRUE, cluster_cols = TRUE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize=5)
 
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters4)
```


#k means, remove na
Protein_Breast <- na.omit(Protein_Breast)
maxclust <- 5
for(maxclust in c(2:maxclust)) {
 
  main <- paste("result for ", maxclust, " clusters", sep="")
  hmx.parameters5 <- list(Protein_Breast, 
                         color = col.pal,
                         cellwidth = 4, cellheight = 5, scale = "none",
                         treeheight_row = 200,
                         kmeans_k = maxclust,
                         show_rownames = T, show_colnames = T, 
                         main = main,
                         clustering_method = "average",
                         cluster_rows = TRUE, cluster_cols = TRUE,
                         clustering_distance_rows = drows1, 
                         clustering_distance_cols = dcols1)
  kmean.hm <- do.call("pheatmap", hmx.parameters5)
  do.call("pheatmap", hmx.parameters5)
  clustnum <- kmean.hm[["kmeans"]][["cluster"]]
  clustered.Protein_Breast <- cbind(Protein_Breast, clustnum)
  last <- ncol(clustered.Protein_Breast)-1
}



  filename <- paste("Clustered.for.", maxclust, "-clusters.tsv", sep="")
  outfile <- paste(basedir, filename, sep="/")
  
  write.table(clustered.Protein_Breast, file=outfile, quote = FALSE, sep="\t", 
              col.names = T, row.names = T)
 
  # plot 'maxclust' cluster detailed heatmap's
  clustered.Protein_Breast <- as.data.frame(clustered.Protein_Breast)
  
  for (clust in 1:maxclust){
    # sample data
    cluster <- subset(clustered.Protein_Breast,    clustered.Protein_Breast$clustnum==clust)[1:last]
 
    # prepare output
    filename <- paste("cluster.", clust, "_of_", maxclust,".pdf", sep="")
    outfile <- paste(basedir, filename, sep="/")
 
    main <- paste("cluster #", clust, " of #", maxclust, sep="")
 
    cluster.parameters6 <- list(cluster,
                               color = col.pal,
                               cellwidth = 4, cellheight = 5,
                               scale = "none",
                               treeheight_row = 200,
                               kmeans_k = NA,
                               show_rownames = T, show_colnames = T, 
                               main = main,
                               clustering_method = "average",
                               cluster_rows = TRUE, cluster_cols = TRUE,
                               clustering_distance_rows = drows1,
                               clustering_distance_cols = dcols1)
    do.call("pheatmap", cluster.parameters6)
    do.call("pheatmap", c(cluster.parameters6, filename=outfile))
  }
}
 
  




**above**


### other ways to make heatmap

```{r eval=TRUE, results='hold'}
# 画图
#rc.PB <- rainbow(nrow(Protein_Breast), start = 0, end = .3)
#cc.PB <- rainbow(ncol(Protein_Breast), start = 0, end = .3)
#hv.PB <- heatmap(
#  Protein_Breast, col = cm.colors(256), scale = "column",
#  RowSideColors = rc.PB, ColSideColors = cc.PB, margins = c(5,10),
#  xlab = " ", ylab =  " ",
#  main = "Protein_Breast"
#)
```

```{r eval=TRUE, results='hold'}
#rc.RB <- rainbow(nrow(RNA_Breast), start = 0, end = .3)
#cc.RB <- rainbow(ncol(RNA_Breast), start = 0, end = .3)
#hv.RB <- heatmap.2(
#  RNA_Breast, col = cm.colors(256), scale = "column",
#  RowSideColors = rc.RB, ColSideColors = cc.RB, margins = c(5,10),
#  xlab = " ", ylab =  " ",
#  main = "RNA_Breast"
#)
```


# 第三幅图
# =====================
Protein_Breast <- read.csv('Protein_Breast.csv', stringsAsFactors = FALSE)
RNA_Breast <- read.csv('RNA_Breast.csv', stringsAsFactors = FALSE)
pam50_genes <- read.csv('pam50_genes.csv', stringsAsFactors = FALSE)

colnames(Protein_Breast) <- paste0(colnames(Protein_Breast), '_pro')
colnames(RNA_Breast) <- paste0(colnames(RNA_Breast), '_rna')

data <- merge(pam50_genes, Protein_Breast, by.x = 'gene', by.y = 'X_pro', all.x = TRUE)
data <- merge(data, RNA_Breast, by.x = 'gene', by.y = 'X_rna', all.x = TRUE)

row.names(data) <- data$gene
data <- select(data, -gene)
data <- as.matrix(data)

rc <- rainbow(nrow(data), start = 0, end = .3)
cc <- rainbow(ncol(data), start = 0, end = .3)
hv <- heatmap(
  data, col = cm.colors(256), scale = "column",
  RowSideColors = rc, ColSideColors = cc, margins = c(5,10),
  xlab = " ", ylab =  " ",
  main = "data"
)






