---
title: "Scatter plots for all gene pairs(R and GPU codes)"
author: "Shuyang"
date: "11/2/2019"
output: 
  html_document: default
  pdf_document: default
---

```{r setDefault, include=FALSE}
# This code chunk defines the default chunks setting
knitr::opts_chunk$set(eval=TRUE, comment="$$$", fig.width=6,fig.height = 3)
```
<br>
```{r eval=TRUE, results='hold'}
library(tidyverse)
```

```{r eval=TRUE, results='hold'}
## 读取数据
setwd('/Users/dengshuyang/Desktop/Bioinfo2019/Breast_project/')
Protein_cormat <- read.csv('Protein_cormat.csv', stringsAsFactors = FALSE)
RNA_cormat <- read.csv('RNA_cormat.csv', stringsAsFactors = FALSE)

Protein_Breast <- read.csv('Protein_Breast.csv', header=TRUE)
RNA_Breast <- read.csv('RNA_Breast.csv', header=TRUE)
```
### Rename row and col names
```{r eval=TRUE, results='hold'}
getName <- function(x){
  v <- unlist(strsplit(x, '\\.'))
  name <- paste0(v[1], '-', v[2])
  return(name)
}
```

```{r eval=TRUE, results='hold'}
getName2 <- function(x){
  w <- unlist(strsplit(x, '\\-'))
  w2 <- w[1]
  return(w2)
}
```

<br>
### columns rename
```{r eval=TRUE, results='hold'}
colnames(CNA_Breast)[2:ncol(CNA_Breast)] <- sapply(colnames(CNA_Breast)[-1], getName)
colnames(Protein_Breast)[2:ncol(Protein_Breast)] <- sapply(colnames(Protein_Breast)[-1], getName)
colnames(RNA_Breast)[2:ncol(RNA_Breast)] <- sapply(colnames(RNA_Breast)[-1], getName)
```
### rename the first col 
```{r eval=TRUE, results='hold'}
Protein_Breast[,1] <- sapply(as.character(Protein_Breast[,1]), getName2)
```
### and then make it the rowname of data frame

```{r eval=TRUE, results='hold'}
Protein_Breast_2 <- Protein_Breast[,-1]
rownames(Protein_Breast_2) <- make.names(Protein_Breast[,1], unique=TRUE)
Protein_Breast <- Protein_Breast_2

CNA_Breast_2 <- CNA_Breast[,-1]
rownames(CNA_Breast_2) <- make.names(CNA_Breast[,1], unique=TRUE)
CNA_Breast <- CNA_Breast_2

RNA_Breast_2 <- RNA_Breast[,-1]
rownames(RNA_Breast_2) <- make.names(RNA_Breast[,1], unique=TRUE)
RNA_Breast <- RNA_Breast_2

```

```{r eval=TRUE, results='hold'}
# ## RNA_cormat 删除 X. 行列数据
#RNA_cormat <- RNA_cormat %>% select(-X.) %>% filter(X != 'X.')
```

```{r eval=TRUE, results='hold'}
## 数据处理
# gene.r表示行基因, gene.c 表示列基因 最终数据匹配为(gene.r, gene.c)
# 列转行

Protein_cormat.tran <- Protein_cormat %>% 
  gather(key, value, -X) %>%
  select(gene.r = X, gene.c = key, Protein_value = value)
RNA_cormat.tran <- RNA_cormat %>% 
  gather(key, value, -X) %>% 
  select(gene.r = X, gene.c = key, RNA_value = value)

## write method in prince gpu
#Protein_cormat_tran <- gather(Protein_cormat, key, value, -rn)
#Protein_cormat_tran <- select(Protein_cormat_tran, gene.r=rn, gene.c=key, Protein_value=value)
#RNA_cormat_tran <- gather(RNA_cormat, key, value, -rn)
#RNA_cormat_tran <- select(RNA_cormat_tran, gene.r=rn, gene.c=key, #RNA_value=value)
```

```{r eval=TRUE, results='hold'}
## 数据合并
plot.data <- Protein_cormat.tran %>% 
  inner_join(
    RNA_cormat.tran, 
    by = c("gene.r", "gene.c")
  )
## write in hpc gpu
#plot_data <- inner_join(Protein_cormat_tran, RNA_cormat_tran, by = c('gene.r', 'gene.c'))
```

```{r eval=TRUE, results='hold'}
## remove na
plot.data <- plot.data %>% filter(!is.na(Protein_value)) %>% 
  filter(!is.na(RNA_value))
## write in hpc
#plot_data <- filter(plot_data, !is.na(Protein_value))
#plot_data <- filter(plot_data, !is.na(RNA_value))
```
<br>
#Make table for pro-rna scatterplot: when r(protein)=1, and r(protein)=-1
```{r eval=TRUE, results='hold'}
table_protein1 <- plot.data %>% filter(Protein_value == 1)
table_protein2 <-  plot.data %>% filter(Protein_value == -1)
# remove same rows contain gene1 and gene2
remove <- which(table_protein1$gene.r==table_protein1$gene.c)
table_protein1 <- table_protein1[-remove,]
#write.csv(table_protein1, file='table_protein1.csv')
#write.csv(table_protein2, file='table_protein2.csv')
```


### add 2 cols of sample number to table_protein1 (rna)
table: protein=1/-1, add 2 columns which are the number of RNA and protein sample (na and 1 are considered as na)
```{r eval=TRUE, results='hold'}
#gene.r
n=1
#b <- matrix(rep(NA,nrow(plot.data)),ncol =1 )
b <- matrix(rep(NA,nrow(table_protein1)),ncol =1 )
#d <- data.frame(matrix(NA, nrow=nrow(table_protein1), ncol=ncol(RNA_Breast)))
#colnames(d) <- colnames(RNA_Breast)
for(i in table_protein1[,"gene.r"]){
  #d[i, ]<- RNA_Breast[i, 1:ncol(RNA_Breast)]
  c <- RNA_Breast[i, 1:ncol(RNA_Breast)]
  #print(d[i,])
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

}
sample_number1 <- as.data.frame(b) 
colnames(sample_number1) <- 'RNA_sample_number.r'
sample_number1



#gene.c

n=1
#b <- matrix(rep(NA,nrow(plot.data)),ncol =1 )
b <- matrix(rep(NA,nrow(table_protein1)),ncol =1 )
#d <- data.frame(matrix(NA, nrow=nrow(table_protein1), ncol=ncol(RNA_Breast)))
#colnames(d) <- colnames(RNA_Breast)
for(i in table_protein1[,"gene.c"]){
  #d[i, ]<- RNA_Breast[i, 1:ncol(RNA_Breast)]
  c <- RNA_Breast[i, 1:ncol(RNA_Breast)]
  #print(d[i,])
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

 
}
sample_number2 <- as.data.frame(b) 
colnames(sample_number2) <- 'RNA_sample_number.c'
sample_number2
```



```{r eval=TRUE, results='hold'}
#combine 2 new cols with original one
table_protein1_num <- cbind(table_protein1, sample_number1)
table_protein1_num2 <- cbind(table_protein1_num, sample_number2)
```

### add 2 cols of sample number to table_protein1 (protein)
```{r eval=TRUE, results='hold'}
#gene.r
n=1
#b <- matrix(rep(NA,nrow(plot.data)),ncol =1 )
b <- matrix(rep(NA,nrow(table_protein1)),ncol =1 )
for(i in table_protein1[,"gene.r"]){
  c <- Protein_Breast[i, 1:ncol(Protein_Breast)]
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

}
sample_number3 <- as.data.frame(b) 
colnames(sample_number3) <- 'Protein_sample_number.r'
sample_number3

table_protein1_num3 <- cbind(table_protein1_num2, sample_number3)
```


```{r eval=TRUE, results='hold'}
#gene.c

n=1
b <- matrix(rep(NA,nrow(table_protein1)),ncol =1 )

for(i in table_protein1[,"gene.c"]){
  #d[i, ]<- RNA_Breast[i, 1:ncol(RNA_Breast)]
  c <- Protein_Breast[i, 1:ncol(Protein_Breast)]
  #print(d[i,])
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

 
}
sample_number4 <- as.data.frame(b) 
colnames(sample_number4) <- 'Protein_sample_number.c'
sample_number4

table_protein1_num4 <- cbind(table_protein1_num3, sample_number4)
```
```{r eval=TRUE, results='hold'}
#write.csv(table_protein1_num4, file='9_highcor_andsamplenumber_tables/table_protein1_num4.csv')
```



### add 2 cols of sample number to table_protein2 (protein)

```{r eval=TRUE, results='hold'}
#gene.r
n=1
#b <- matrix(rep(NA,nrow(plot.data)),ncol =1 )
b <- matrix(rep(NA,nrow(table_protein2)),ncol =1 )
for(i in table_protein2[,"gene.r"]){
  c <- Protein_Breast[i, 1:ncol(Protein_Breast)]
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

}
sample_number5 <- as.data.frame(b) 
colnames(sample_number5) <- 'Protein_sample_number.r'
sample_number5

table_protein2_num5 <- cbind(table_protein2, sample_number5)
```


```{r eval=TRUE, results='hold'}
#gene.c
n=1
b <- matrix(rep(NA,nrow(table_protein2)),ncol =1 )

for(i in table_protein2[,"gene.c"]){
  #d[i, ]<- RNA_Breast[i, 1:ncol(RNA_Breast)]
  c <- Protein_Breast[i, 1:ncol(Protein_Breast)]
  #print(d[i,])
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1
}
sample_number6 <- as.data.frame(b) 
colnames(sample_number6) <- 'Protein_sample_number.c'
sample_number6

table_protein2_num6 <- cbind(table_protein2_num5, sample_number6)
```

### add 2 cols of sample number to table_protein2 (rna)

```{r eval=TRUE, results='hold'}
#gene.r
n=1
b <- matrix(rep(NA,nrow(table_protein2)),ncol =1 )
for(i in table_protein2[,"gene.r"]){
  c <- RNA_Breast[i, 1:ncol(RNA_Breast)]
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1

}
sample_number7 <- as.data.frame(b) 
colnames(sample_number7) <- 'RNA_sample_number.r'
sample_number7

table_protein2_num7 <- cbind(table_protein2_num6, sample_number7)
```


```{r eval=TRUE, results='hold'}
#gene.c
n=1
b <- matrix(rep(NA,nrow(table_protein2)),ncol =1 )

for(i in table_protein2[,"gene.c"]){
  c <- RNA_Breast[i, 1:ncol(RNA_Breast)]
  b[n,1] <- as.vector(apply(c, 1, function(x) length(which(!is.na(x)))))
  n=n+1
}
sample_number8 <- as.data.frame(b) 
colnames(sample_number8) <- 'RNA_sample_number.c'
sample_number8

table_protein2_num8 <- cbind(table_protein2_num7, sample_number8)
```


```{r eval=TRUE, results='hold'}
#write.csv(table_protein2_num8, file='9_highcor_andsamplenumber_tables/table_protein2_num8.csv')
```
#  Choose 5 point at each corner(4) of pro-rna scatterplot and then make point plots of RNA correlation, protein correlation
# 1. RNA correlation
```{r eval=TRUE, results='hold'}
#rna
rightdown <- plot.data %>% filter(RNA_value>0.55 & Protein_value< -0.55) %>% select(-Protein_value)
rightdown <- rightdown[order(rightdown$RNA_value,decreasing=TRUE),][1:5,]

rightup <- plot.data %>% filter(RNA_value>0.8 & Protein_value> 0.8 & RNA_value<1.0) %>% select(-Protein_value)
rightup <- rightup[order(rightup$RNA_value,decreasing=TRUE),][1:8,]

leftdown <- plot.data %>% filter(RNA_value< -0.5 & Protein_value< -0.5) %>% select(-Protein_value)
leftdown <- leftdown[order(leftdown$RNA_value,decreasing=TRUE),][1:7,]

leftup <- plot.data %>% filter(RNA_value< -0.5 & Protein_value> 0.7) %>% select(-Protein_value)
leftup <- leftup[order(leftup$RNA_value,decreasing=TRUE),][1:6,]

#protein
rightdown2 <- plot.data %>% filter(RNA_value>0.5 & Protein_value< -0.5) %>% select(-RNA_value)
rightdown2 <- rightdown2[order(rightdown2$Protein_value,decreasing=TRUE),][1:7,]

rightup2 <- plot.data %>% filter(RNA_value>0.8 & Protein_value> 0.8 & RNA_value<1.0) %>% select(-RNA_value)
rightup2 <- rightup2[order(rightup2$Protein_value,decreasing=TRUE),][1:8,]

leftdown2 <- plot.data %>% filter(RNA_value< -0.5 & Protein_value< -0.6) %>% select(-RNA_value)
leftdown2 <- leftdown2[order(leftdown2$Protein_value,decreasing=TRUE),][1:8,]

leftup2 <- plot.data %>% filter(RNA_value< -0.5 & Protein_value> 0.7) %>% select(-RNA_value)
leftup2 <- leftup2[order(leftup2$Protein_value,decreasing=TRUE),][1:6,]
```

```{r eval=TRUE, results='hold'}
#rna1
#gene.r
n=1
c1 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c1) <- colnames(RNA_Breast)
for(i in rightdown[,"gene.r"]){
  c1[i,] <- RNA_Breast[i,]

}
c1
```
```{r eval=TRUE, results='hold'}
#rna1
#gene.c
n=1
c2 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c2) <- colnames(RNA_Breast)
for(i in rightdown[,"gene.c"]){
  c2[i,] <- RNA_Breast[i,]

}
c2
```
```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/rd_rna.jpeg')
rd_rna <- matplot(t(c1),t(c2), pch = 1, type = "p", col =1:5)
#dev.off()
```

```{r eval=TRUE, results='hold'}
#rna2
#gene.r
n=1
c3 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c3) <- colnames(RNA_Breast)
for(i in rightup[,"gene.r"]){
  c3[i,] <- RNA_Breast[i,]

}
c3
#gene.c
n=1
c4 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c4) <- colnames(RNA_Breast)
for(i in rightup[,"gene.c"]){
  c4[i,] <- RNA_Breast[i,]

}
c4
#matplot(t(c3),t(c4), pch = 1, type = "p", col =1:5, main='RNA_rightup')
```

```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/ru_rna.jpeg')
ru_rna <- matplot(t(c3),t(c4), pch = 1, type = "p", col =1:5)
#dev.off()
```


```{r eval=TRUE, results='hold'}
#rna3
#gene.r
n=1
c5 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c5) <- colnames(RNA_Breast)
for(i in leftdown[,"gene.r"]){
  c5[i,] <- RNA_Breast[i,]

}
c5
#gene.c
n=1
c6 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c6) <- colnames(RNA_Breast)
for(i in leftdown[,"gene.c"]){
  c6[i,] <- RNA_Breast[i,]

}
c6
```
```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/ld_rna.jpeg')
ld_rna <- matplot(t(c5),t(c6), pch = 1, type = "p", col =1:5)
#dev.off()
```

```{r eval=TRUE, results='hold'}
#rna4
#gene.r
n=1
c7 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c7) <- colnames(RNA_Breast)
for(i in leftup[,"gene.r"]){
  c7[i,] <- RNA_Breast[i,]

}
c7
#gene.c
n=1
c8 <- data.frame(matrix(nrow=0, ncol=ncol(RNA_Breast)))#make a blank df
colnames(c8) <- colnames(RNA_Breast)
for(i in leftup[,"gene.c"]){
  c8[i,] <- RNA_Breast[i,]

}
c8
```

```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/lu_rna.jpeg')
lu_rna <- matplot(t(c7),t(c8), pch = 1, type = "p", col =1:5)
#dev.off()
```

# 2. protein correlation
```{r eval=TRUE, results='hold'}
#protein1
#gene.r
n=1
p1 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p1) <- colnames(Protein_Breast)
for(i in rightdown2[,"gene.r"]){
  p1[i,] <- Protein_Breast[i,]

}
p1
#gene.c

p2 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p2) <- colnames(Protein_Breast)
for(i in rightdown2[,"gene.c"]){
  p2[i,] <- Protein_Breast[i,]

}
p2
```
```{r eval=TRUE, results='hold'}
jpeg('gene_pair_plots/rd_pro.jpeg')
rd_pro <- matplot(t(p1),t(p2), pch = 1, type = "p", col =1:5)
dev.off()
```


```{r eval=TRUE, results='hold'}
#protein2
#gene.r
p3 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p3) <- colnames(Protein_Breast)
for(i in rightup2[,"gene.r"]){
  p3[i,] <- Protein_Breast[i,]

}
p3
#gene.c

p4 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p4) <- colnames(Protein_Breast)
for(i in rightup2[,"gene.c"]){
  p4[i,] <- Protein_Breast[i,]

}
p4
```
```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/ru_pro.jpeg')
ru_pro <- matplot(t(p3),t(p4), pch = 1, type = "p", col =1:5)
#dev.off()
```

```{r eval=TRUE, results='hold'}
#protein3
#gene.r
p5 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p5) <- colnames(Protein_Breast)
for(i in leftdown2[,"gene.r"]){
  p5[i,] <- Protein_Breast[i,]

}
p5
#gene.c

p6 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p6) <- colnames(Protein_Breast)
for(i in leftdown2[,"gene.c"]){
  p6[i,] <- Protein_Breast[i,]

}
p6
```
```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/ld_pro.jpeg')
ld_pro <- matplot(t(p5),t(p6), pch = 1, type = "p", col =1:5)
#dev.off()
```


```{r eval=TRUE, results='hold'}
#protein4
#gene.r
p7 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p7) <- colnames(Protein_Breast)
for(i in leftup2[,"gene.r"]){
  p7[i,] <- Protein_Breast[i,]

}
p7
#gene.c

p8 <- data.frame(matrix(nrow=0, ncol=ncol(Protein_Breast)))#make a blank df
colnames(p8) <- colnames(Protein_Breast)
for(i in leftup2[,"gene.c"]){
  p8[i,] <- Protein_Breast[i,]

}
p8
```
```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/lu_pro.jpeg')
lu_pro <- matplot(t(p7),t(p8), pch = 1, type = "p", col =1:5)
#dev.off()
```
# Make table for r(R1, P2), r(R2, P1) under condition r(R1, P1) < 0.3, etc… (only in pro-ran scatterplot)
```{r eval=TRUE, results='hold'}
pro_rna_cor <- cor(plot.data[sapply(plot.data,1, is.numeric)])
```

## 画图
## when so much point run on gpu, how to make scatter plot more clear to avoid big black hole-like picture:
https://stackoverflow.com/questions/37381684/ggplot-alpha-levels-appear-different-on-fill-and-border-of-points-ringing-artef


```{r eval=TRUE, results='hold'}
#jpeg('gene_pair_plots/combined.jpeg')
par(mfrow=c(2,4))
#rna
matplot(t(c1),t(c2), pch = 1, type = "p", col =1:5, main='RNA_rightdown')
matplot(t(c3),t(c4), pch = 1, type = "p", col =1:5, main='RNA_rightup')
matplot(t(c5),t(c6), pch = 1, type = "p", col =1:5, main='RNA_leftdown')
matplot(t(c7),t(c8), pch = 1, type = "p", col =1:5, main='RNA_leftup')
#pro
matplot(t(p1),t(p2), pch = 1, type = "p", col =1:5, main='Protein_rightdown')
matplot(t(p3),t(p4), pch = 1, type = "p", col =1:5, main='Protein_rightup')
matplot(t(p5),t(p6), pch = 1, type = "p", col =1:5, main='Protein_leftdown')
matplot(t(p7),t(p8), pch = 1, type = "p", col =1:5, main='Protein_leftup')

#dev.off()
```

```{r}
#jpeg('gene_pair_plots/leftup_rna_legend.jpeg')
col_set <- rainbow(ncol(t(c7)))
matplot(t(c7),t(c8), pch = 1, type = "p",col = col_set, main='RNA_leftup')
legend( 5, c("C7orf63", "B4GALT2", "CCNG1", "CCNE1","C5orf15"),col =col_set, pch=1)
#dev.off()
```
---------
library(tidyverse)
library(dplyr)
library(data.table)
#install.packages('dtplyr')
#library(dtplyr)
library(lubridate)

#Protein_cormat_tran <- read.csv('Protein_cormat_tran.csv', stringsAsFactors=FALSE)
#Protein_cormat_tran <- select(Protein_cormat_tran, -X)
RNA_cormat_tran <- read.csv('RNA_cormat_tran.csv', stringsAsFactors=FALSE)
RNA_cormat_tran <- select(RNA_cormat_tran, -X)
CNA_cormat_tran <- read.csv('CNA_cormat_tran.csv', stringsAsFactors=FALSE)
CNA_cormat_tran <- select(CNA_cormat_tran, -X)

plot_data <- inner_join(RNA_cormat_tran, CNA_cormat_tran, by = c('gene.r', 'gene.c'))

plot_data <- filter(plot_data, !is.na(RNA_value))
plot_data <- filter(plot_data, !is.na(CNA_value))

#write.csv(plot_data, file='plot_data.csv')

pro_rna_scatter <- ggplot(plot_data, aes(x = RNA_value, y = CNA_value)) +
  geom_point(alpha = 0.3) +
  xlim(-1, 1) +ylim(-1, 1) +
  xlab("RNA value") +
  ylab("CNA value") +
  ggtitle("gene pairs correlation of rna-cna")
ggsave('rna_cna_scatter.jpeg')







