---
title: "1113breast make gene pairs scatter plot for ERBB2, CCNB1, and CENPF separatly"
author: "Shuyang"
date: "11/12/2019"
output: html_document: default
  pdf_document: default
---

```{r setDefault, include=FALSE}
# This code chunk defines the default chunks setting
knitr::opts_chunk$set(eval=TRUE, comment="$$$", fig.width=6,fig.height = 3)
```
<br>
```{r eval=FALSE}
library(tidyverse)
library(dplyr)
library(data.table)
library(lubridate)
```

```{r eval=TRUE, results='hold'}
setwd('/Users/dengshuyang/Desktop/Bioinfo2019/Breast_project/')
CNA_Breast <- read.csv('CNA_Breast.csv', header=TRUE)
Protein_Breast <- read.csv('Protein_Breast.csv', header=TRUE)
RNA_Breast <- read.csv('RNA_Breast.csv', header=TRUE)
```

### Rename row and col names
```{r eval=TRUE, results='hold'}
getName <- function(x){
  v <- unlist(strsplit(x, '\\.'))
  name <- paste0(v[1], '-', v[2])
  return(name)
}
```

```{r eval=TRUE, results='hold'}
getName2 <- function(x){
  w <- unlist(strsplit(x, '\\-'))
  w2 <- w[1]
  return(w2)
}
```

<br>
### columns rename
```{r eval=TRUE, results='hold'}
colnames(CNA_Breast)[2:ncol(CNA_Breast)] <- sapply(colnames(CNA_Breast)[-1], getName)
colnames(Protein_Breast)[2:ncol(Protein_Breast)] <- sapply(colnames(Protein_Breast)[-1], getName)
colnames(RNA_Breast)[2:ncol(RNA_Breast)] <- sapply(colnames(RNA_Breast)[-1], getName)
```
### rename the first col 
```{r eval=TRUE, results='hold'}
Protein_Breast[,1] <- sapply(as.character(Protein_Breast[,1]), getName2)
```
### and then make it the rowname of data frame

```{r eval=TRUE, results='hold'}
Protein_Breast_2 <- Protein_Breast[,-1]
rownames(Protein_Breast_2) <- make.names(Protein_Breast[,1], unique=TRUE)
Protein_Breast <- Protein_Breast_2

CNA_Breast_2 <- CNA_Breast[,-1]
rownames(CNA_Breast_2) <- make.names(CNA_Breast[,1], unique=TRUE)
CNA_Breast <- CNA_Breast_2

RNA_Breast_2 <- RNA_Breast[,-1]
rownames(RNA_Breast_2) <- make.names(RNA_Breast[,1], unique=TRUE)
RNA_Breast <- RNA_Breast_2

```
<br>
# make gene pairs scatter plot for ERBB2, CCNB1, and CENPF separatly
```{r eval=TRUE, results='hold'}
tProtein_Breast <- t(Protein_Breast)
tCNA_Breast <- t(CNA_Breast)
tRNA_Breast <- t(RNA_Breast)

tProtein_Breast <- as.data.frame(tProtein_Breast)
tCNA_Breast <- as.data.frame(tCNA_Breast)
tRNA_Breast <- as.data.frame(tRNA_Breast)
```

### 1. ERBB2 pairs
```{r eval=TRUE, results='hold'}
#protein ERBB2
ERBB2_pro <- as.numeric(tProtein_Breast[,'ERBB2'])
ERBB2_cor_pro <- apply(tProtein_Breast,2, function(x){cor(ERBB2_pro,x)})
ERBB2_procor <- as.data.frame(ERBB2_cor_pro, header=FALSE)
ERBB2_procor <- na.omit(ERBB2_procor)
ERBB2_procor <- setDT(ERBB2_procor, keep.rownames = TRUE)[]
ERBB2_procor <- ERBB2_procor[order(ERBB2_procor$ERBB2_cor_pro, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
#RNA ERBB2
ERBB2_rna <- as.numeric(tRNA_Breast[,'ERBB2'])
ERBB2_cor_rna <- apply(tRNA_Breast,2, function(x){cor(ERBB2_rna,x)})
ERBB2_rnacor <- as.data.frame(ERBB2_cor_rna, header=FALSE)
ERBB2_rnacor <- na.omit(ERBB2_rnacor)
ERBB2_rnacor <- setDT(ERBB2_rnacor, keep.rownames = TRUE)[]
ERBB2_rnacor <- ERBB2_rnacor[order(ERBB2_rnacor$ERBB2_cor_rna, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
# CNA ERBB2
ERBB2_cna <- as.numeric(tCNA_Breast[,'ERBB2'])
ERBB2_cor_cna <- apply(tCNA_Breast,2, function(x){cor(ERBB2_cna,x)})
ERBB2_cnacor <- as.data.frame(ERBB2_cor_cna, header=FALSE)
ERBB2_cnacor <- na.omit(ERBB2_cnacor)
ERBB2_cnacor <- setDT(ERBB2_cnacor, keep.rownames = TRUE)[]
ERBB2_cnacor <- ERBB2_cnacor[order(ERBB2_cnacor$ERBB2_cor_cna, decreasing = FALSE),]
```
# 1-1.pro-rna ERBB2 pairs scatter plot
```{r eval=TRUE, results='hold'}
# pro-rna
plot.data1 <- ERBB2_procor %>% 
  inner_join(
    ERBB2_rnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
ERBB2_pro_rna <- ggplot(plot.data1, aes(x = ERBB2_cor_rna, y = ERBB2_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("Protein value") + 
  ggtitle("ERBB2 RNA-protein")+
  theme(plot.title=element_text(size=22))
ERBB2_pro_rna
#ggsave('ERBB2_pro_rna.jpeg')
```
## make table to show high cor for both pro and rna with ERBB2
```{r eval=TRUE, results='hold'}
highprorna_erbb2 <- plot.data1 %>% filter(ERBB2_cor_pro>0.7 & ERBB2_cor_rna> 0.7) 

highprorna_erbb2 <- highprorna_erbb2[order(highprorna_erbb2$ERBB2_cor_pro,decreasing=TRUE),] 
#write.csv(highprorna_erbb2, file='9_highcor_tables/highprorna_erbb2.csv')
```

# 1-2. cna-rna ERBB2 pairs scatter plot
```{r eval=TRUE, results='hold'}
# cna-rna
plot.data2 <- ERBB2_cnacor %>% 
  inner_join(
    ERBB2_rnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
ERBB2_cna_rna <- ggplot(plot.data2, aes(x = ERBB2_cor_rna, y = ERBB2_cor_cna)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("CNA value") + 
  ggtitle("ERBB2 RNA-CNA")+
  theme(plot.title=element_text(size=22))
ERBB2_cna_rna
#ggsave('ERBB2_cna_rna.jpeg')
```

```{r eval=TRUE, results='hold'}
highcnarna_erbb2 <- plot.data2 %>% filter(ERBB2_cor_cna>0.7 & ERBB2_cor_rna> 0.7) 

highcnarna_erbb2 <- highcnarna_erbb2[order(highcnarna_erbb2$ERBB2_cor_cna,decreasing=TRUE),] 
#write.csv(highcnarna_erbb2, file='9_highcor_tables/highcnarna_erbb2.csv')
```

# 1-3. cna-pro ERBB2 pairs scatter plot
```{r eval=TRUE, results='hold'}
# cna-pro
plot.data3 <- ERBB2_cnacor %>% 
  inner_join(
    ERBB2_procor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
ERBB2_cna_pro <- ggplot(plot.data3, aes(x = ERBB2_cor_cna, y = ERBB2_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("CNA value") + 
  ylab("Protein value") + 
  ggtitle("ERBB2 CNA-protein")+
  theme(plot.title=element_text(size=22))
ERBB2_cna_pro
#ggsave('gene_pair_plots/ERBB2_cna_pro.jpeg')
```

```{r eval=TRUE, results='hold'}
highcnapro_erbb2 <- plot.data3 %>% filter(ERBB2_cor_pro>0.3 & ERBB2_cor_cna> 0.3) 

highcnapro_erbb2 <- highcnapro_erbb2[order(highcnapro_erbb2$ERBB2_cor_cna,decreasing=TRUE),] 
write.csv(highcnapro_erbb2, #file='9_highcor_andsamplenumber_tables/highcnapro_erbb2.csv')
```


# CCNB1 pairs
```{r eval=TRUE, results='hold'}
# CNA CCNB1
CCNB1_cna <- as.numeric(tCNA_Breast[,'CCNB1'])
CCNB1_cor_cna <- apply(tCNA_Breast,2, function(x){cor(CCNB1_cna,x)})
CCNB1_cnacor <- as.data.frame(CCNB1_cor_cna, header=FALSE)
CCNB1_cnacor <- na.omit(CCNB1_cnacor)
CCNB1_cnacor <- setDT(CCNB1_cnacor, keep.rownames = TRUE)[]
CCNB1_cnacor <- CCNB1_cnacor[order(CCNB1_cnacor$CCNB1_cor_cna, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
# RNA CCNB1
CCNB1_rna <- as.numeric(tRNA_Breast[,'CCNB1'])
CCNB1_cor_rna <- apply(tRNA_Breast,2, function(x){cor(CCNB1_rna,x)})
CCNB1_rnacor <- as.data.frame(CCNB1_cor_rna, header=FALSE)
CCNB1_rnacor <- na.omit(CCNB1_rnacor)
CCNB1_rnacor <- setDT(CCNB1_rnacor, keep.rownames = TRUE)[]
CCNB1_rnacor <- CCNB1_rnacor[order(CCNB1_rnacor$CCNB1_cor_rna, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
# Protein CCNB1
# delete na for calculate correlations
CCNB1_pro <- as.numeric(tProtein_Breast[,'CCNB1'])
CCNB1_pro <- na.omit(CCNB1_pro)
```

```{r eval=TRUE, results='hold'}
# to keep compatible dimensions, delete samples(rows) where CCNB1 is NA
tProtein_Breast <-tProtein_Breast[-c(27, 28,29, 78, 79, 80),]
CCNB1_cor_pro <- apply(tProtein_Breast,2, function(x){cor(CCNB1_pro,x)})
```

```{r eval=TRUE, results='hold'}
CCNB1_procor <- as.data.frame(CCNB1_cor_pro, header=FALSE)
CCNB1_procor <- na.omit(CCNB1_procor)
CCNB1_procor <- setDT(CCNB1_procor, keep.rownames = TRUE)[]
CCNB1_procor <- CCNB1_procor[order(CCNB1_procor$CCNB1_cor_pro, decreasing = FALSE),]
```
# 2-1 pro-rna CCNB1 pairs scatter plot 
```{r eval=TRUE, results='hold'}
# pro-rna
plot.data4 <- CCNB1_procor %>% 
  inner_join(
    CCNB1_rnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CCNB1_rna_pro <- ggplot(plot.data4, aes(x = CCNB1_cor_rna, y = CCNB1_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("Protein value") + 
  ggtitle("CCNB1 RNA-protein")+
  theme(plot.title=element_text(size=22))
CCNB1_rna_pro
#ggsave('gene_pair_plots/CCNB1_rna_pro.jpeg')
```

```{r eval=TRUE, results='hold'}
highprorna_ccnb1 <- plot.data4 %>% filter(CCNB1_cor_pro>0.6 & CCNB1_cor_rna> 0.6) 

highprorna_ccnb1 <- highprorna_ccnb1[order(highprorna_ccnb1$CCNB1_cor_pro,decreasing=TRUE),] 
#write.csv(highprorna_ccnb1, file='9_highcor_tables/highprorna_ccnb1.csv')
```

# 2-2 pro-cna CCNB1 pairs scatter plot 
```{r eval=TRUE, results='hold'}
# pro-cna
plot.data5 <- CCNB1_procor %>% 
  inner_join(
    CCNB1_cnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CCNB1_cna_pro <- ggplot(plot.data5, aes(x = CCNB1_cor_cna, y = CCNB1_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("CNA value") + 
  ylab("Protein value") + 
  ggtitle("CCNB1 CNA-protein")+
  theme(plot.title=element_text(size=22))
CCNB1_cna_pro
#ggsave('gene_pair_plots/CCNB1_cna_pro.jpeg')
```
```{r eval=TRUE, results='hold'}
highprocna_ccnb1 <- plot.data5 %>% filter(CCNB1_cor_cna> 0.75) 

highprocna_ccnb1 <- highprocna_ccnb1[order(highprocna_ccnb1$CCNB1_cor_pro,decreasing=TRUE),] 
#write.csv(highprocna_ccnb1, file='9_highcor_tables/highprocna_ccnb1.csv')
```

# 2-3 rna-cna CCNB1 pairs scatter plot 
```{r eval=TRUE, results='hold'}
# rna-cna
plot.data6 <- CCNB1_rnacor %>% 
  inner_join(
    CCNB1_cnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CCNB1_rna_cna <- ggplot(plot.data6, aes(x = CCNB1_cor_rna, y = CCNB1_cor_cna)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("CNA value") + 
  ggtitle("CCNB1 RNA-CNA")+
  theme(plot.title=element_text(size=22))
CCNB1_rna_cna
#ggsave('gene_pair_plots/CCNB1_rna_cna.jpeg')
```

```{r eval=TRUE, results='hold'}
highrnacna_ccnb1 <- plot.data6 %>% filter(CCNB1_cor_cna> 0.75 & CCNB1_cor_rna>0.75) 

highrnacna_ccnb1 <- highrnacna_ccnb1[order(highrnacna_ccnb1$CCNB1_cor_rna,decreasing=TRUE),] 
#write.csv(highrnacna_ccnb1, file='9_highcor_tables/highrnacna_ccnb1.csv')
```


# CENPF pairs
```{r eval=TRUE, results='hold'}
# rna CENPF
CENPF_rna <- as.numeric(tRNA_Breast[,'CENPF'])
CENPF_cor_rna <- apply(tRNA_Breast,2, function(x){cor(CENPF_rna,x)})
CENPF_rnacor <- as.data.frame(CENPF_cor_rna, header=FALSE)
CENPF_rnacor <- na.omit(CENPF_rnacor)
CENPF_rnacor <- setDT(CENPF_rnacor, keep.rownames = TRUE)[]
CENPF_rnacor <- CENPF_rnacor[order(CENPF_rnacor$CENPF_cor_rna, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
# CNA CENPF
CENPF_cna <- as.numeric(tCNA_Breast[,'CENPF'])
CENPF_cor_cna <- apply(tCNA_Breast,2, function(x){cor(CENPF_cna,x)})
CENPF_cnacor <- as.data.frame(CENPF_cor_cna, header=FALSE)
CENPF_cnacor <- na.omit(CENPF_cnacor)
CENPF_cnacor <- setDT(CENPF_cnacor, keep.rownames = TRUE)[]
CENPF_cnacor <- CENPF_cnacor[order(CENPF_cnacor$CENPF_cor_cna, decreasing = FALSE),]
```

```{r eval=TRUE, results='hold'}
# protein CENPF
CENPF_pro <- as.numeric(tProtein_Breast[,'CENPF'])
CENPF_cor_pro <- apply(tProtein_Breast,2, function(x){cor(CENPF_pro,x)})
CENPF_procor <- as.data.frame(CENPF_cor_pro, header=FALSE)
CENPF_procor <- na.omit(CENPF_procor)
CENPF_procor <- setDT(CENPF_procor, keep.rownames = TRUE)[]
CENPF_procor <- CENPF_procor[order(CENPF_procor$CENPF_cor_pro, decreasing = FALSE),]
```
# 3-1 pro-rna CENPF pairs scatter plot 
```{r eval=TRUE, results='hold'}
# rna-cna
plot.data7 <- CENPF_rnacor %>% 
  inner_join(
    CENPF_procor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CENPF_rna_pro <- ggplot(plot.data7, aes(x = CENPF_cor_rna, y = CENPF_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("Protein value") + 
  ggtitle("CENPF RNA-protein")+
  theme(plot.title=element_text(size=22))
CENPF_rna_pro
#ggsave('gene_pair_plots/CENPF_rna_pro.jpeg')
```

```{r eval=TRUE, results='hold'}
highprorna_cenpf <- plot.data7 %>% filter(CENPF_cor_rna> 0.7 & CENPF_cor_pro>0.7) 

highprorna_cenpf <- highprorna_cenpf[order(highprorna_cenpf$CENPF_cor_rna,decreasing=TRUE),] 
#write.csv(highprorna_cenpf, file='9_highcor_tables/highprorna_cenpf.csv')
```

# 3-2 pro-cna CENPF pairs scatter plot 
```{r eval=TRUE, results='hold'}
# pro-cna
plot.data8 <- CENPF_cnacor %>% 
  inner_join(
    CENPF_procor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CENPF_cna_pro <- ggplot(plot.data8, aes(x = CENPF_cor_cna, y = CENPF_cor_pro)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("CNA value") + 
  ylab("Protein value") + 
  ggtitle("CENPF CNA-protein")+
  theme(plot.title=element_text(size=22))
CENPF_cna_pro
#ggsave('gene_pair_plots/CENPF_cna_pro.jpeg')
```
```{r eval=TRUE, results='hold'}
highprocna_cenpf <- plot.data8 %>% filter(CENPF_cor_cna> 0.6 & CENPF_cor_pro>0.5) 

highprocna_cenpf <- highprocna_cenpf[order(highprocna_cenpf$CENPF_cor_cna,decreasing=TRUE),] 
#write.csv(highprocna_cenpf, file='9_highcor_tables/highprocna_cenpf.csv')
```

# 3-3 rna-cna CENPF pairs scatter plot 
```{r eval=TRUE, results='hold'}
# rna-cna
plot.data9 <- CENPF_cnacor %>% 
  inner_join(
    CENPF_rnacor, 
    by = 'rn'
  )
```

```{r eval=TRUE, results='hold'}
CENPF_cna_rna <- ggplot(plot.data9, aes(x = CENPF_cor_rna, y = CENPF_cor_cna)) +
  geom_point(alpha = 0.3, size=1, stroke=0)+
  xlim(-1, 1) + 
  ylim(-1, 1) + 
  xlab("RNA value") + 
  ylab("CNA value") + 
  ggtitle("CENPF RNA-CAN")+
  theme(plot.title=element_text(size=22))
CENPF_cna_rna
#ggsave('gene_pair_plots/CENPF_cna_rna.jpeg')
```
```{r eval=TRUE, results='hold'}
highrnacna_cenpf <- plot.data9 %>% filter(CENPF_cor_cna> 0.75 & CENPF_cor_rna>0.7) 

highrnacna_cenpf <- highrnacna_cenpf[order(highrnacna_cenpf$CENPF_cor_cna,decreasing=TRUE),] 
#write.csv(highrnacna_cenpf, file='9_highcor_tables/highrnacna_cenpf.csv')
```

```{r}
#library(ggpubr)
ggarrange(ERBB2_pro_rna, ERBB2_cna_rna, ERBB2_cna_pro, CCNB1_rna_pro, CCNB1_rna_cna, CCNB1_cna_pro, CENPF_rna_pro, CENPF_cna_rna, CENPF_cna_pro + rremove("x.text"), 
          labels = c("A", "B", "C",'D', 'E', 'F', 'G', 'H'),
          ncol = 3, nrow = 3)
```





