---
title: "heatmap_1021"
author: "Shuyang"
date: "10/21/2019"
output: 
  html_document: default
  pdf_document: default
---

```{r setDefault, include=FALSE}
# This code chunk defines the default chunks setting
knitr::opts_chunk$set(eval=TRUE, comment="$$$", fig.width=6)
```
<br>
```{r eval=TRUE}
library(plyr);library(dplyr)
library(tidyverse)
library(tidyr)
library(colorspace)
library(data.table)
library(gplots)
library( "genefilter" )
library(ggplot2)
library(NMF)
library(pkgmaker)
library(registry)
library(rngtools)
library(cluster)

library('heatmap.plus')
library('gplots')
library('RColorBrewer')
library("pheatmap")
library(viridis)

```
<br>
```{r eval=TRUE, results='hold'}
# 数据导入
setwd('/Users/dengshuyang/Desktop/Bioinfo2019/Breast_project/')
Protein_Breast <- read.csv('Protein_Breast_2.csv', stringsAsFactors = FALSE)
RNA_Breast <- read.csv('RNA_Breast_2.csv', stringsAsFactors = FALSE)
CNA_Breast <- read.csv('CNA_Breast_2.csv', stringsAsFactors = FALSE)
pam50_genes <- read.csv('pam50_genes.csv', stringsAsFactors = FALSE)
```

```{r eval=TRUE, results='hold'}
# 数据筛选
Protein_Breast <- merge(pam50_genes, Protein_Breast, by.y = 'X', by.x = 'gene') #inner join if don't use all.x=TRUE
RNA_Breast <- merge(pam50_genes, RNA_Breast, by.y = 'X', by.x = 'gene', all.x = TRUE)
CNA_Breast <- merge(pam50_genes, CNA_Breast, by.y='X', by.x='gene')
```

```{r eval=TRUE, results='hold'}
# 数据转换
row.names(Protein_Breast) <- Protein_Breast$gene
Protein_Breast <- select(Protein_Breast, -gene) 

row.names(RNA_Breast) <- RNA_Breast$gene
RNA_Breast <- select(RNA_Breast, -gene)

rownames(CNA_Breast) <- CNA_Breast$gene
CNA_Breast <- select(CNA_Breast, -gene)
```
### rename column 
```{r eval=TRUE, results='hold'}
getName <- function(x){
  v <- unlist(strsplit(x, '\\.'))
  name <- paste0(v[1], '-', v[2])
  return(name)
}
```

```{r eval=TRUE, results='hold'}
colnames(CNA_Breast) <- sapply(colnames(CNA_Breast), getName)
colnames(Protein_Breast) <- sapply(colnames(Protein_Breast), getName)
colnames(RNA_Breast) <- sapply(colnames(RNA_Breast), getName)
```


```{r eval=TRUE, results='hold'}
tProtein_Breast <- t(Protein_Breast)
tCNA_Breast <- t(CNA_Breast)
tRNA_Breast <- t(RNA_Breast)

tProtein_Breast <- as.data.frame(tProtein_Breast)
tCNA_Breast <- as.data.frame(tCNA_Breast)
tRNA_Breast <- as.data.frame(tRNA_Breast)


```

```{r eval=TRUE, results='hold'}
# make correlation matrix with pearson method
Protein_cormat <- round(cor(tProtein_Breast, use='p', method='pearson'), 10)
#head(Protein_cormat) #matrix
CNA_cormat <- round(cor(tCNA_Breast, use='p', method='pearson'), 10)
RNA_cormat <- round(cor(tRNA_Breast, use='p', method='pearson'), 10)
```

```{r eval=TRUE, results='hold'}
# make correlation matrix with spearman method
Protein_cormat2 <- round(cor(tProtein_Breast, use='p', method = 'spearman'), 10)
#head(Protein_cormat) #matrix
CNA_cormat2 <- round(cor(tCNA_Breast, use='p', method='spearman'), 10)
RNA_cormat2 <- round(cor(tRNA_Breast, use='p', method='spearman'), 10)
```
### make heatmap
```{r eval=TRUE, results='hold'}
# Protein-protein
paletteLength <- 10
col.pal <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
#col.pal <- brewer.pal(9,"Blues")
drows1 <- "euclidean"
dcols1 <- "euclidean"

hm.parameters_protein <- list(Protein_cormat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "Protein-Protein heatmap",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 10,
  fontsize_row = 5,
  fontsize_col = 5
  )
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_protein)
```

```{r eval=TRUE, results='hold'}
#RNA-RNA

hm.parameters_RNA <- list(RNA_cormat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = 'none',
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-RNA heatmap",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 10,
  fontsize_row = 5,
  fontsize_col = 5)
 
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_RNA)
```

```{r eval=TRUE, results='hold'}
#CNA-CNA
hm.parameters_CNA <- list(CNA_cormat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "CNA-CNA heatmap",
  clustering_method = "average",
  cluster_rows = F, cluster_cols = F,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize=10,
  fontsize_row = 5,
  fontsize_col = 5)
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_CNA)
```
<br>

pam50_genes <- read.csv('pam50_genes.csv', stringsAsFactors = FALSE)
pam50_genes <- pam50_genes[order(pam50_genes$gene),]
pam50_list <- as.list(pam50_genes)

RNA-CNA
rna_cna_cormat=matrix(NA, length(pam50_list), length(pam50_list))
for(gene_rna in pam50_list){
  #print(gene_rna)
  if(gene_rna %in% colnames(tRNA_Breast)){
    #print(gene_rna)
    for(gene_cna in pam50_list){
      if(gene_cna %in% colnames(tCNA_Breast)){
        rna_cna_cormat <- rbind(round(cor(tRNA_Breast[gene_rna],
                                                      tCNA_Breast[gene_cna],
                                                      use='p',
                                                      
                                                      method='pearson'), 10))

      }
    }
    
  }
}


```{r eval=TRUE, results='hold'}
#make csv from python for heatmap use
rmbracket1 <- function(x){
  w <- unlist(strsplit(x, "\\'"))
  w2 <- w[2]
  return(w2)
}

rmbracket2 <- function(x){
  w <- unlist(strsplit(x, "\\)"))
  w2 <- w[1]
  return(w2)
}
```

```{r eval=TRUE, results='hold'}
# load data and remove symbols
#rna_cna <- read.csv('rna_cna.csv',header=FALSE, stringsAsFactors = FALSE)
#pro_rna <- read.csv('pro_rna.csv',header=FALSE, stringsAsFactors = FALSE)
rna_cna_spearman <- read.csv('rna_cna_spearman.csv',header=FALSE, stringsAsFactors = FALSE)
pro_rna_spearman <- read.csv('rna_cna_spearman.csv',header=FALSE, stringsAsFactors = FALSE)
```

```{r eval=TRUE, results='hold'}
#rna_cna$V1 <- sapply(rna_cna$V1, rmbracket1)
#rna_cna$V2 <- sapply(rna_cna$V2, rmbracket1)
#rna_cna$V3 <- sapply(rna_cna$V3, rmbracket2)

rna_cna_spearman$V1 <- sapply(rna_cna_spearman$V1, rmbracket1)
rna_cna_spearman$V2 <- sapply(rna_cna_spearman$V2, rmbracket1)
rna_cna_spearman$V3 <- sapply(rna_cna_spearman$V3, rmbracket2)

#pro_rna$V1 <- sapply(pro_rna$V1, rmbracket1)
#pro_rna$V2 <- sapply(pro_rna$V2, rmbracket1)
#pro_rna$V3 <- sapply(pro_rna$V3, rmbracket2)

pro_rna_spearman$V1 <- sapply(pro_rna_spearman$V1, rmbracket1)
pro_rna_spearman$V2 <- sapply(pro_rna_spearman$V2, rmbracket1)
pro_rna_spearman$V3 <- sapply(pro_rna_spearman$V3, rmbracket2)
```

```{r eval=TRUE, results='hold'}
# diffrenciate x and y as rna and cna
#rna_cna$V1 <- paste0(rna_cna$V1, '_rna')
#rna_cna$V2 <- paste0(rna_cna$V2, '_cna')

rna_cna_spearman$V1 <- paste0(rna_cna_spearman$V1, '_rna')
rna_cna_spearman$V2 <- paste0(rna_cna_spearman$V2, '_cna')

# diffrenciate x and y as pro and rna
#pro_rna$V1 <- paste0(pro_rna$V1, '_pro')
#pro_rna$V2 <- paste0(pro_rna$V2, '_rna')

pro_rna_spearman$V1 <- paste0(pro_rna_spearman$V1, '_pro')
pro_rna_spearman$V2 <- paste0(pro_rna_spearman$V2, '_rna')
```

```{r eval=TRUE, results='hold'}
# convert csv to data_frame, putting rna and cna gene name in x and y axis
#temp <- data.frame(x=rna_cna$V1,
                   #y=rna_cna$V2,
                   #z=rna_cna$V3)

#r_c_mat <- spread(temp, y,z )

temp_spearman <- data.frame(x=rna_cna_spearman$V1,
                   y=rna_cna_spearman$V2,
                   z=rna_cna_spearman$V3)

r_c_mat_spearman <- spread(temp_spearman, y,z )
```

```{r eval=TRUE, results='hold'}
# convert csv to data_frame, putting pro and rna gene name in x and y axis
#temp2 <- data.frame(x=pro_rna$V2,
                   #y=pro_rna$V1,
                   #z=pro_rna$V3)

#p_r_mat <- spread(temp2, y,z )

temp_spearman2 <- data.frame(x=pro_rna_spearman$V2,
                   y=pro_rna_spearman$V1,
                   z=pro_rna_spearman$V3)

p_r_mat_spearman <- spread(temp_spearman2, y,z )
```


```{r eval=TRUE, results='hold'}
#rename rows
#rownames(r_c_mat) <- r_c_mat$x
#r_c_mat <- select(r_c_mat, -x)

#rownames(p_r_mat) <- p_r_mat$x
#p_r_mat <- select(p_r_mat, -x)

rownames(r_c_mat_spearman) <- r_c_mat_spearman$x
r_c_mat_spearman <- select(r_c_mat_spearman, -x)

rownames(p_r_mat_spearman) <- p_r_mat_spearman$x
p_r_mat_spearman <- select(p_r_mat_spearman, -x)
```

```{r eval=TRUE, results='hold'}
#replace all nan as NA for removing 
#r_c_mat[r_c_mat == ' nan'] <- NA # there is a space before nan
#p_r_mat[p_r_mat == ' nan'] <- NA # there is a space before nan

r_c_mat_spearman[r_c_mat_spearman == ' nan'] <- NA # there is a space before nan
p_r_mat_spearman[p_r_mat_spearman == ' nan'] <- NA # there is a space before nan
```

```{r eval=TRUE, results='hold'}
# remove rows which contains all NA values
#r_c_mat <- r_c_mat[!(rowSums(is.na(r_c_mat))==ncol(r_c_mat)),]
#p_r_mat <- p_r_mat[!(rowSums(is.na(p_r_mat))==ncol(p_r_mat)),]

r_c_mat_spearman <- r_c_mat_spearman[!(rowSums(is.na(r_c_mat_spearman))==ncol(r_c_mat_spearman)),]
p_r_mat_spearman <- p_r_mat_spearman[!(rowSums(is.na(p_r_mat_spearman))==ncol(p_r_mat_spearman)),]
```

```{r eval=TRUE, results='hold'}
# remove cols which contains all NA values
#r_c_mat <- r_c_mat[, !(colSums(is.na(r_c_mat))==nrow(r_c_mat))]
#p_r_mat <- p_r_mat[, !(colSums(is.na(p_r_mat))==nrow(p_r_mat))]

r_c_mat_spearman <- r_c_mat_spearman[, !(colSums(is.na(r_c_mat_spearman))==nrow(r_c_mat_spearman))]
p_r_mat_spearman <- p_r_mat_spearman[, !(colSums(is.na(p_r_mat_spearman))==nrow(p_r_mat_spearman))]
```

```{r eval=TRUE, results='hold'}
# convert to mumeric for picturing heatmap
#r_c_mat[] <- lapply(r_c_mat, function(x) as.numeric(as.character(x)))
#p_r_mat[] <- lapply(p_r_mat, function(x) as.numeric(as.character(x)))

r_c_mat_spearman[] <- lapply(r_c_mat_spearman, function(x) as.numeric(as.character(x)))
p_r_mat_spearman[] <- lapply(p_r_mat_spearman, function(x) as.numeric(as.character(x)))
```


```{r eval=TRUE, results='hold'}
#r_c_mat <- as.matrix(r_c_mat)
#p_r_mat <- as.matrix(p_r_mat)

r_c_mat_spearman <- as.matrix(r_c_mat_spearman)
p_r_mat_spearman <- as.matrix(p_r_mat_spearman)
```



```{r eval=TRUE, results='hold'}
# RNA-CNA heatmap with pearson
hm.parameters_r_c <- list(r_c_mat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-CNA heatmap",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 10,
  fontsize_row = 5,
  fontsize_col = 5
  )
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_r_c)
```


```{r eval=TRUE, results='hold'}
# RNA-CNA heatmap with same order of x and y with pearson
hm.parameters_r_c_order <- list(r_c_mat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-CNA heatmap",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 5
  )
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_r_c_order)
```

```{r eval=TRUE, results='hold'}
# RNA-CNA heatmap with spearman
hm.parameters_r_c_spearman <- list(r_c_mat_spearman, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-CNA heatmap",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 5
  )
```
```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_r_c_spearman)
```



```{r eval=TRUE, results='hold'}
# Protein_RNA heatmap with same order of x and y
# which is to change cluster_rows and cluster_cols to FALSE
paletteLength <- 10
col.pal <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
hm.parameters_p_r_order <- list(p_r_mat, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-protein heatmap (pearson)",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 10,
  fontsize_row = 5,
  fontsize_col = 5
  )
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_p_r_order)
```

```{r eval=TRUE, results='hold'}
# Protein_RNA heatmap with spearman
paletteLength <- 10
col.pal <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
hm.parameters_p_r_spearman <- list(p_r_mat_spearman, 
  color = col.pal,
  cellwidth = 4, cellheight = 5, scale = "none",
  treeheight_row = 200,
  kmeans_k = NA,
  show_rownames = T, show_colnames = T,
  main = "RNA-protein heatmap (spearman)",
  clustering_method = "average",
  cluster_rows = FALSE, cluster_cols = FALSE,
  clustering_distance_rows = drows1, 
  clustering_distance_cols = dcols1,
  fontsize = 10,
  fontsize_row = 5,
  fontsize_col = 5
  )
```

```{r eval=TRUE, results='hold'}
do.call("pheatmap", hm.parameters_p_r_spearman)
```

### spearman doesn't generate much 'nan' as pearson does

